---
title: "01_Reading_in_spatial_data"
author: "Reed Kenny"
date: "2023-05-31"
output: html_document
---

# Reading in Spatial Data

In this workshop we will look at dowloading species occurence data and plotting it with US forest service administrative boundary layers. 

We will first download some points from the [Global Biodiveristy Information Facitlity](gbif.org). We will use the package rgbif to access the api. 

```{r} 

library(rgbif)

J.saximontanus <- occ_search(scientificName = "Juncus saximontanus", hasCoordinate = TRUE)

J.sax.points <- J.saximontanus$data %>% select("scientificName", "occurrenceRemarks", "locality", "associatedTaxa", "habitat", "recordedBy", "eventDate", "decimalLongitude", "decimalLatitude")
```

Since gbif includes many columns of data in the download I have gone ahead and only selected those that may be relevant. 

The next thing we can do is to use the sf (simple features) package to convert the columns of latitude and longitude data from GBIF into something that R will recognize as spatial data. 

```{r} 
library(sf)

J.sax.points <- J.sax.points %>% st_as_sf(coords = c("decimalLongitude","decimalLatitude"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84")

```

Notice here that I had to tell sf which columns are longitude and latitude, (the format is x, y) and I had to specify a CRS (coordinate reference system). When in doubt, most data generated after about 1990 is likley using the WGS 84 system, it's what all GPS units use.

Next we can use the really nifty package mapview, to quickly look at what we downloaded and make sure it makes sense. 

```{r}

library(mapview)

mapview(J.sax.points)

```

Ok that looks good so now I can pull in a few other layers. I am interested in California occurences of this species, as well as eventually making a map with the California border. So I want to get the California outline on a map. The tigris package is really good for US administrative boundaries as well as a ton of other things like census tract data. For now lets just use it to get the California border. 

```{r} 

library(tigris)

CA <- states() %>% filter(NAME =="California")

```

That was easy, now lets see if it worked



```{r}

mapview(CA)

```

Next I want to download the US national forest boundaries as well as ranger district boundaries. 

These I will have to pull from the [USFS website](https://data.fs.usda.gov/geodata/edw/datasets.php?dsetCategory=boundaries)




