---
title: "02_Spatial_analyses"
author: "Reed Kenny"
date: "2023-06-01"
output: html_document
---

# Spatial Analyses

Awesome! We have a bunch of spatial data layers now, we can do cool stuff with them right ...?

```{r eval = FALSE} 

library(sf)

J.sax.cal <- st_intersection(J.sax.points, CA)

```

Oooops! Looks like our CRS systems are not matching, so we need to transform one. Let's use WGS for everything. I'm just going to copy/paste my CRS definition that I used for the GBIF data. 

```{r eval = FALSE} 

CA <- st_transform(CA, crs = "+proj=longlat +datum=WGS84 +ellps=WGS84")

```
Ok lets try again

```{r eval = FALSE}
library(mapview)

J.sax.cal <- st_intersection(J.sax.points, CA)

mapview(J.sax.cal)

```
Great, that worked. Now lets also get only the forest boundaries and ranger districts in California. 

```{r eval = FALSE}

US_forests <- US_forests %>% st_transform(crs = "+proj=longlat +datum=WGS84 +ellps=WGS84")

districts <- districts %>% st_transform(crs = "+proj=longlat +datum=WGS84 +ellps=WGS84")

Cal_forests <- st_intersection(US_forests, CA)

```
Dang! We were being so careful... looks like a geometry error. This is saying that two polygons are sharing a vertex which is does not like. We can try the function st_make_valid, which checks the geometry and will correct situations like this (*hopefully*)

```{r eval = FALSE}

US_forests <- st_make_valid(US_forests)

districts <- st_make_valid(districts)

```

Ok lets try again

```{r eval = FALSE}

Cal_forests <- st_intersection(US_forests, CA)

Cal_districts <- st_intersection(districts, CA)



```

Great, the last analysis thing I want to do is to add the ranger district information to my Juncus points. You could do this with a left join but then I think you would end up with multiple columns of spatial data and it might not work. 

```{r eval = FALSE}

J.sax.cal <- st_join(J.sax.cal, Cal_districts)

View(J.sax.cal)

```

