---
title: "03_mapping"
author: "Reed Kenny"
date: "2023-06-01"
output: html_document
---

# Mapping

Ok lets put these all together in a map

```{r eval = FALSE}

library(tmap)

#tmap_mode("view")
tmap_mode("plot")
tm_basemap("OpenTopoMap") +
tm_shape(CA, bbox = "San Bernardino National Forest") +
  tm_borders("black", lwd = .5) +
tm_shape(Cal_forests) +
  tm_polygons(col = "FORESTNAME", palette = "Blues",
              title = "National Forest") +
tm_shape(Cal_districts) +
  tm_borders("white", lwd = .5) +
  tm_shape(J.sax.cal) +
  tm_dots(col = "red") +
  tm_scale_bar(breaks = c(0, 1, 2), text.size = 1, position = c("left", "bottom")) +
  tm_compass(type = "4star", position = c("left", "bottom"))  +
  tm_layout(main.title = "Juncus saximontanus sites California", 
            main.title.size = 1.25, main.title.position="center",
            legend.outside = TRUE, legend.outside.position = "right",
            frame = FALSE, legend.width = 3)

```

Thats pretty rad, what if we just want to zoom in on part of the map? We have a few options with tmap. The extend of the map matched the extect of the first layer that you add, so we can make a new layer if we want that corresponds to our area of interest. 

Let's say we want to zoom in on the Big Bear region. 



```{r eval = FALSE}

Bigbear <- Cal_districts %>% filter(ADMINFORES == "99051200010343")

tmap_mode("view")
tm_basemap("OpenTopoMap") +
  tm_shape(Bigbear) +
  tm_borders("black") +
tm_shape(J.sax.cal) +
  tm_dots(col = "red")
  

```

Ok not that bad, but I'd rather be centered on the cluster of points. You can manually set the bounding box to achieve this

```{r eval = FALSE}
tmap_mode("view")
tm_basemap("OpenTopoMap") +
  tm_shape(Cal_districts, bbox = c(-117.60450, 33.96786, -116.63543, 34.41352)) +
  tm_borders("black") +
tm_shape(J.sax.cal) +
  tm_dots(col = "red")

```
